Response to reviewers

### 2022-05-10 paper/paper.tex
Edited Dewi's part, 3 comments remains.

Statistics and data science education relies on cleaned and simplified data, suitably called textbook data, for clear examples about how to apply different techniques. An example of this is the wages data made public by Singer and Willett (2003) in their book, ``Applied longitudinal data analysis,'' which can be used to teach generalized linear models, in addition to hierarchical, mixed effects, and multilevel models. The data records hourly wages of a sample of high school dropouts from 1979-1994, along with the demographic variables, such as education and race, taken from the National Longitudinal Survey of Youth (NLSY79) (Bureau of Labor Statistics, U.S. Department of Labor 2021a).

The story from modeling the data (and as reported by Singer and Willett) is that wages increase with the length of time in the workforce, a higher level of education leads to higher wages, and that race makes a difference, on average. However, an exploratory analysis reveals that the individual experience varies a great deal from the overall average. Some individuals experience a decline in wages the longer they are in the workforce, and many experience volatility in their wages. The wages data was used to illustrate exploratory longitudinal data analysis in Ilk (2004), and was further developed into a case study for use in the teaching of exploratory data analysis at Iowa State University.

This disparity between the average and the individual is a part of statistics as a discipline that requires more attention. This particular data set is a prime example of discussing this disparity. Textbook data sets have longevity if there is an unresolved mystery. The iris data (Andereson 1935) is a prime example. It has withstood the test of time because the three species cannot be perfectly classified, and so it continues to challenge researchers and instructors to do better in the analysis (a side note: the iris data is best replaced today with the penguins data (Horst, Hill, and Gorman 2020), which has similar qualities, is new, and does not suffer from a connection with eugenics (Stodel 2020)). We argue the wages data is in this class of textbook data, too, because it presents a challenge for longitudinal data analysis: how can we better summarize and explain the individual experience?

For statistics and data science by association, it is increasingly important to reach the individual. One might describe this as a divergence of purpose -- statistics for public policy -- or statistics for the public. The two are not the same. As the world becomes more electronically connected, combating misinformation and mitigating conspiracy theories require statistics that address the individual. For example, with the wages data, even though the message for public policy is that demographic profile is related to different wage patterns on average, the message for the individual is you are more than your demographic. The majority of people in the study do not have a pattern that is similar to the average. If you have a bad experience, that your wages have declined over time, you are not alone; there are others like you, and more than you think. A similar tone is echoed occasionally in the public media. For example, an article published in the Sydney Morning Herald argues there is no average Australian (Moncrief 2015).

As a textbook data set, though, the wages data is outdated. The most recent year in the data is 1994, 10 years prior to when Singer and Willett (2003) was published. Teachers of statistics need contemporary data sets to show how techniques are relevant for today's students. Using tired old textbook data sets can imbue a misconception that the field is not current. The wages data is extracted from NSLY79, one of the best examples of open data, which is constantly being updated. It should be possible to continuously refresh the textbook data from the data repository. This paper describes our (non-glamorous) journey from open (Open Knowledge Foundation 2021) wild data to textbook data.

@@

According to Wickham (2014), tidy data sets comply with three rules: (i) each variable forms a column, (ii) each observation forms a row, and (iii) each type of observational unit forms a table. The raw data, \texttt{new\_data\_qnames}, does not comply with these rules as it is organized such that each row corresponds to an individual. As respondents can have multiple jobs at specific years, the column names, such as \texttt{HRP1\_1979}, \texttt{HRP2\_1979}, \texttt{HRP1\_1980} and \texttt{HRP2\_1980}, contain the information about the job number up to 5 (\texttt{HRP1} = job 1, \texttt{HRP2} = job 2) and the year. The raw data consequently has a large number of columns (770 to be specific). The values in the cell under the variables begin with \texttt{HRP} correspond to the hourly wage in dollars. A glimpse of this data shows:

\begin{verbatim}
#> 'data.frame':    12686 obs. of  770 variables:
#>  $ CASEID_1979                               : int  1 2 3 4 5 6 7 8 ...
#>  $ HRP1_1979                                 : int  328 385 365 NA 310 NA NA NA ...
#>  $ HRP2_1979                                 : int  NA NA NA NA 375 NA NA NA ...
#>  $ HRP3_1979                                 : int  NA NA 275 NA NA NA NA NA ...
#>  $ HRP4_1979                                 : int  NA NA NA NA NA 250 NA NA ...
#>  $ HRP5_1979                                 : int  NA NA NA NA NA NA NA NA ...
#>  $ HRP1_1980                                 : int  NA 457 397 NA 333 275 300 394 ...
#>  $ HRP2_1980                                 : int  NA NA 367 NA NA NA NA NA ...
#>  $ HRP3_1980                                 : int  NA NA 380 NA NA NA 290 NA ...
#>  $ HRP4_1980                                 : int  NA NA NA NA NA NA NA NA ...
#>   [list output truncated]
\end{verbatim}

@@

\caption{\label{tab:gender-race-table}Contingency table for gender and race for the full NLSY79 data. The percentage (rounded to closest 1\%) is out of the total corresponding to row.}
\centering
\begin{tabular}[t]{lrrrr}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{3}{c}{Race} & \multicolumn{1}{c}{ } \\
\cmidrule(l{3pt}r{3pt}){2-4}
Gender & Hispanic & Black & Non-Black, Non-Hispanic & Total\\
\midrule
Male & 1,000 (16\%) & 1,613 (25\%) & 3,790 (59\%) & 6,403\\
Female & 1,002 (16\%) & 1,561 (25\%) & 3,720 (59\%) & 6,283\\
\midrule
Total & 2,002 (16\%) & 3,174 (25\%) & 7,510 (59\%) & 12,686\\
\bottomrule
\end{tabular}
\end{table}

@@

This paper has illustrated the steps and decisions made to take a particular open data set and make it a textbook data set, ready for the classroom or research. In the first stage, we showed the steps performed to get the data from the NLSY79 database. The data format was converted to a tidy format for more flexibility in cleaning and exploring. Initial data analysis was conducted to investigate and screen the quality of the data. We found and provided a fix for many anomalous observations in wages using a robust linear regression model. The refreshed data is compared with the original set using a variety of numerical summaries and graphics. The current subset is made available in a new R package, called \texttt{yowie}.

The data cleaning process is documented, and the code has been made available. These provide the opportunity to again refresh the textbook data as new data is published into the NLSY79 database.
Determining an appropriate robustness weight from which to threshold unusual observations was conducted using a \texttt{shiny} (Chang et al. 2020) app, and the choices used in the refreshed data are documented.

@@

Why is this exercise important for teachers and students? This work illustrates the steps in cleaning and processing data in preparation for it to be a textbook data set. Choices made during the cleaning and processing can affect findings made with the data, and these should be transparent. Along with the textbook data, which is now provided as an R package, the documentation of the process provides some examples for teaching data cleaning, initial data analysis, and exploratory data analysis. The refreshed textbook data provides a resource for teaching longitudinal data analysis.

@@

\hypertarget{refs}{}
\leavevmode\hypertarget{ref-iris-data}{}%
Andereson, Edgar. 1935. ``The Irises of the Gaspe Peninsula.'' \emph{Bulletin of the American Iris Society} 59: 2--5.

>>>>

Statistics and data science education relies on cleaned and simplified data, suitably called textbook data, for clear examples about how to apply different techniques. An example of this is the wages data made public by Singer and Willett (2003) in their book, ``Applied longitudinal data analysis,'' which can be used to teach generalized linear models, and additionally hierarchical, mixed effects, and multilevel models. The data records hourly wages of a sample of high school dropouts from 1979-1994, along with the demographic variables, such as education and race, taken from the National Longitudinal Survey of Youth (NLSY79) (Bureau of Labor Statistics, U.S. Department of Labor 2021a).

The story from modeling the data (and as reported by Singer and Willett) is that wages increase with the length of time in the workforce, a higher level of education leads to higher wages, and that race makes a difference, on average. However, an exploratory analysis reveals that the individual experience varies a great deal from the overall average. Some individuals experience a decline in wages the longer they are in the workforce, and many experience volatility in their wages. It is for these reasons that the wages data was used to illustrate exploratory longitudinal data analysis in Ilk (2004), and was further developed into a case study for use in the teaching of exploratory data analysis at Iowa State University.

This disparity between the overall trend and the individual heterogeneity is what makes this data interesting. Textbook data sets have longevity if they have unresolved elements. The iris data (Anderson 1935) is a prime example. It has withstood the test of time because the three species cannot be perfectly classified, and so it continues to challenge researchers and instructors to do better in the analysis. (It should be noted that the iris data is best replaced today with the penguins data (Horst, Hill, and Gorman 2020), which has similar qualities, is new, and does not suffer from a connection with eugenics (Stodel 2020)). We argue that the wages data is in this class of textbook data, too, because it presents a challenge for longitudinal data analysis: how can we better summarize and explain the individual experience?

For statistics, and data science by association, it is increasingly important to reach the individual. One might think of this as a divergence of purpose -- statistics for public policy -- or statistics for the public. The two are not the same. As the world becomes more electronically connected, combating misinformation and mitigating conspiracy theories require statistics that address the individual. For example, with the wages data, the overall trend, across demographics, is a steady increase in wages, but the patterns among individuals is heterogeneous. Some individuals see a decline in their wages, some an increase, some have dramatic ups and downs from year to year, and the heterogeneity of the patterns are evident across demographics. Subject-specific variation explains most of the variation in wages, and even though the overall trend is statistically significant, it is weak. The message for public policy is that demographic profile is related to different wage patterns on average and some structural social change is desirable. However, discussing the overall trend with an individual is misleading -- more than likely their pattern is completely different. It could even be depressing for them to compare themselves to the overall average, especially if the individual's wages have a declining trend or high volatility. It would be more useful for an individual to know what percentage of the population have profiles like theirs. We argue that different summaries are needed to communicate with the public, and ones where they might be able to individually act on to change their own situation. We occasionally hear this voiced in the public media media, also, for example, an article published in the Sydney Morning Herald argues there is no average Australian (Moncrief 2015). Thus the wages data provides educators with a challenge, from a methodological and a philosophical perspective, and wage experience is a topic of interest to many.

As a textbook data set, though, the wages data is outdated. The most recent year in the data is 1994, 10 years prior to when Singer and Willett (2003) was published. Teachers of statistics need contemporary data sets to show how techniques are relevant for today's students. Using tired old textbook data sets can imbue a misconception that the field is not current. The wages data is extracted from NSLY79, one of the best examples of open data (see details at Open Knowledge Foundation (2021)), which is constantly being updated. It should be possible to continuously refresh the textbook data from the data repository. This paper describes our (non-glamorous) journey from open wild data to textbook data.

@@

According to Wickham (2014), tidy data sets comply with three rules: (i) each variable forms a column, (ii) each observation forms a row, and (iii) each type of observational unit forms a table. The raw data, \texttt{new\_data\_qnames}, does not comply with these rules as it is organized such that each row corresponds to an individual. As respondents can have multiple jobs at specific years, the column names, such as \texttt{HRP1\_1979}, \texttt{HRP2\_1979}, \texttt{HRP1\_1980} and \texttt{HRP2\_1980}, contain the information about the job number up to 5 (\texttt{HRP1} = job 1, \texttt{HRP2} = job 2) and the year. The raw data consequently has a large number of columns (742 to be specific). The values in the cell under the variables begin with \texttt{HRP} correspond to the hourly wage in dollars. A glimpse of this data shows:

\begin{verbatim}
#> 'data.frame':    12686 obs. of  742 variables:
#>  $ CASEID_1979                               : int  1 2 3 4 5 6 7 8 ...
#>  $ HRP1_1979                                 : int  328 385 365 NA 310 NA NA NA ...
#>  $ HRP2_1979                                 : int  NA NA NA NA 375 NA NA NA ...
#>  $ HRP3_1979                                 : int  NA NA 275 NA NA NA NA NA ...
#>  $ HRP4_1979                                 : int  NA NA NA NA NA 250 NA NA ...
#>  $ HRP5_1979                                 : int  NA NA NA NA NA NA NA NA ...
#>  $ HRP1_1980                                 : int  NA 457 397 NA 333 275 300 394 ...
#>  $ HRP2_1980                                 : int  NA NA 367 NA NA NA NA NA ...
#>  $ HRP3_1980                                 : int  NA NA 380 NA NA NA 290 NA ...
#>  $ HRP4_1980                                 : int  NA NA NA NA NA NA NA NA ...
#>   [list output truncated]
\end{verbatim}

@@

\caption{\label{tab:gender-race-table}Contingency table for sex and race for the full NLSY79 data. The percentage (rounded to closest 1\%) is out of the total corresponding to row.}
\centering
\begin{tabular}[t]{lrrrr}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{3}{c}{Race} & \multicolumn{1}{c}{ } \\
\cmidrule(l{3pt}r{3pt}){2-4}
Sex & Hispanic & Black & Non-Black, Non-Hispanic & Total\\
\midrule
Male & 1,000 (16\%) & 1,613 (25\%) & 3,790 (59\%) & 6,403\\
Female & 1,002 (16\%) & 1,561 (25\%) & 3,720 (59\%) & 6,283\\
\midrule
Total & 2,002 (16\%) & 3,174 (25\%) & 7,510 (59\%) & 12,686\\
\bottomrule
\end{tabular}
\end{table}

@@

Any longitudinal dataset used for education should have a sufficiently reproducible process to be updated with new data. The NLSY79 dataset is a great teaching tool that has become outdated, both because the dataset stops in 1994, and because the demographic data could be handled more delicately. This paper has illustrated the necessary steps and decisions made to take a particular open data set and make it a textbook data set, ready for the classroom or research. In the first stage, we showed the steps performed to get the data from the NLSY79 database. The data format was converted to a tidy format for more flexibility in cleaning and exploring. Initial data analysis was conducted to investigate and screen the quality of the data. We found and provided a fix for many anomalous observations in wages using a robust linear regression model. The refreshed data is compared with the original set using a variety of numerical summaries and graphics. The current subset is made available in a new R package, called \texttt{yowie}.

The data cleaning process is documented, and the code has been made available. These provide the opportunity to again refresh the textbook data as new data is published into the NLSY79 database. Determining an appropriate robustness weight from which to threshold unusual observations was conducted using a \texttt{shiny} (Chang et al. 2020) app, which is provided with the code, and the choices used in the refreshed data are documented.

@@

Why is the work presented here useful for teachers and students? There are several reasons:

\begin{itemize}
\tightlist
\item
  It primarily illustrates the steps in cleaning and processing a well-known longitudinal data so that it can be further refreshed as a textbook data set as new data emerges. Choices made during the cleaning and processing can affect findings made with the data, are transparent, and can be a basis for classroom discussions.
\item
  Some of the methods shown, and lessons learned about the data, can also be considered generally for data cleaning, initial data analysis and exploratory data analysis, useful for working with other data sets.
\item
  The refreshed data can be used for teaching advanced linear modeling, using almost identical code from Singer and Willett (2003), and thus make those lessons more current for today's students.
\item
  It provides the data to develop a case study for teaching exploratory data analysis of longitudinal data, focusing on the individual experience. The vignettes of the \texttt{brolgar} (Tierney, Cook, and Prvan 2020) package provide useful guides for the case study content.
\end{itemize}

@@

\hypertarget{refs}{}
\leavevmode\hypertarget{ref-iris-data}{}%
Anderson, Edgar. 1935. ``The Irises of the Gaspe Peninsula.'' \emph{Bulletin of the American Iris Society} 59: 2--5.

### 2022-05-10 response/response2.Rmd
Edited Dewi's part, 3 comments remains.

It is not clear how to handle this. We interpret the comment from the Editor, that the paper is consistent with the call for the special issue. The AE would like it to be clearly one of three types. The paper does have of each of the three types, which we believe has value. There is some wording in the introduction ("An example of this is the wages data made public by Singer and Willett (2003) in their book, “Applied lon- gitudinal data analysis,” which can be used to teach generalized linear models, in addition to hierarchical, mixed effects, and multilevel models.") and we have added additional text in Section 5 Summary, on lessons learned, to help the reader understand the elements that might be used for their teaching. XXX DONE

@@

We interpret this to mean we should change the variable name in the cleaned data, and so have done this, and then "sex" is uniformly used throughout the paper. XXX Dewi to do

\begin{description}
\item[Associate Editor:] \textcolor{violet}{\textbf{The discussion around highest grade completed is mechanical in what was done, but lacks substantive reasoning for those decisions and possible downstream con- sequences.} It is still unclear to me whether education is measured by year or by category (it’s described both ways) and, in either case, the decision for one or the other isn’t contrasted or justified. For example `hcg` is described as a factor and `grade` is described as only increasing (numeric?) and surely the authors mean non-decreasing. If this is meant to be a case study for the classroom, this decision is rich ground for discussion.}
\end{description}

We have added more explanation of the two variables, and suggestions of where to use one vd the other in classroom analyses. XXX Dewi to do

@@

Using `rlm` with the `nest` and `map` functions from `tidyr`, efficiently and simply fit these models. They can be easily explained in a classroom setting, and equip students generally with advanced data handling skills. Similar results would be obtained from using robustlmm, though. We have removed reference to memory and convergence issues. We have also removed a specific reference to threshold used. Having the particular number used is not important for the explanation of the approach and as we have seen from the review, is distracting for the reader. This section has been modified so that the approach is more understandable. XXX DONE

@@

This is more of a comment than a request to make a change, but we agree that this is an area that could be a good classroom discussion. We have revised the section on handling extremes to make our explanation simpler, with links to the shiny app that we put together to assist in the judgement and choice of threshold. We hope that this provides fodder for discussion. It could definitely be worked into a teaching exercise. XXX DONE

@@

It would be nice if the database contained a broader description of race, but it only has a single variable for race. For this reason, our cleaned data reflects this, and has a single variable for race. XXX Dewi to do

@@

We have revised the introduction to fix this. XXX DONE

@@

We have added additional bullet points on the benefit for educators in Section 5, in response to the overview comments by the Editor and AE (top of this response). We think it is best to keep content on cleaning and tidying the data, in a reproducible manner, to match the mission of the special issue. XXX DONE

@@

We have changed all to "refresh". XXX Dewi

@@

Thanks for this, exactly right! We have changed the wording accordingly, in various places in the paper. XXX DC, ET, NT please check that this message comes across clearly enough.

@@

Same point as made by the AE, and how we have addressed it is described above.

@@

See response above to the associate editor, about this concern. XXX DONE

@@

Done XXX Dewi

@@

XXX Dewi Add some words to make it clear what data this is summarising

@@

We have expanded this explanation XXX Dewi

@@

\begin{description}
\item[Reviewer 2:] \textcolor{violet}{Some extraneous punctuation marks are present}
\begin{itemize}
  \item p1 in abstract: Both “wages textbook subset, have not” and “open source R package, called” do not need commas.
  \item p2 “high school dropouts, from 1979-1994” does not need comma
  \item p2 comma after “divergence of purpose” might be better replaced with dash.
  \item p4 the sentence “Plot (C) shows the profile for an individual, with not such a high maximum wage but still indicates a problem: their wages are consistently low except for one year where they earned close to 1200/hour.” needs a few edits. I suggest “Plot (C) shows the profile for an individual with a maximum wage that is not so extreme but still indicates a problem: their wages are consistently low except for one year where they earned close to 1200/hour.”
  \item p24 “predominately” does not need a hyphen.
\end{itemize}
\end{description}

@@

\begin{description}
\item[Reviewer 2:] \textcolor{violet}{Punctuation should go inside quotation marks, not outside}
\begin{itemize}
\item p2 comma  “Applied longitudinal data analysis”,
\item p4 comma “tame data”,
\item p6 comma “statistical value chain”,
\item p9 period “female”.
\item p13 period “number of weeks worked since the last interview”.
\end{itemize}
\end{description}

@@

\begin{description}
\item[Reviewer 2:] \textcolor{violet}{Miscellaneous comments:} 
\begin{itemize}
\item p6 “For example, use a single categorical race variable instead of the two binary race variables.” Perhaps missing a “we” before use?
\item p6 The sentence beginning “van der Loo and de Jonge” is jarring because of the lowercase name, particularly because it starts a paragraph and section. I recommend flipping the clauses to begin “In the context of official statistics, van der Loo and de Jonge…”
\item p18 “The year when the individual starting to work.” should perhaps be “The year when the individual started to work.”
\item p24 The sentence “On an individual level, one needs to know where I am in this data and does this data relate to me.” needs edits. I’m not sure people from the longitudinal study are likely to be looking at this data, so “where I am in this data” is not quite accurate. Rather, people might want to see how their characteristics relate to those in the dataset. 
\item p26 Cooksey reference should have NLSY capitalized. 
\end{itemize}
\end{description}

@@

\begin{description}
\item[Reviewer 1:] \textcolor{violet}{Minor comments:}
\begin{itemize}
\item P2, l46: missing right parenthesis.
\item P9, l24: missing word(s) "this sometimes difficult the adjustment"
\item P11, l43: "hours" worked
\item P12, l32: unit in "weeks"
\item P14, l38: Figure 3 shows...
\item P21, l21: "the weeks worked since" ...
\item P24, l21: The sentence "On an individual level, one needs to know where I am in this data and does this data relate to me" is awkward. Please revise.
\item P34 l 38: Figure 5 (C) is mislabeled
\end{itemize}
\end{description}

@@

We have put the capitalisation back in, and changed "WHITE" to be "NBH". XXX Dewi

\begin{description}
\item[Reviewer 3:] \textcolor{violet}{Page 7 lines 36-42:}
\begin{itemize}
\item 1. The wages data of the whole NLSY79 cohort, including females.
\item 2. A separate table of the demographic data of the whole NLSY79 cohort.
\item 3. The high school dropouts’ wages data is closest to a refreshed version of Singer and
Willett (2003)’s data.
\end{itemize}
1 and 2 are nouns and 3 is a sentence – I’m a little confused what this third dataset represents.  I think you mean that you create a subset of (1) in the scope of the original data, to see how closely it replicates?
\end{description}

>>>>

* It is not clear how to handle this. We interpret the comment from the Editor, that the paper is consistent with the call for the special issue. The AE would like it to be clearly one of three types. The paper does have of each of the three types, which we believe has value. There is some wording in the introduction ("An example of this is the wages data made public by Singer and Willett (2003) in their book, “Applied lon- gitudinal data analysis,” which can be used to teach generalized linear models, in addition to hierarchical, mixed effects, and multilevel models.") and we have added additional text in Section 5 Summary, on lessons learned, to help the reader understand the elements that might be used for their teaching. XXX DONE

@@

* We interpret this to mean we should change the variable name in the cleaned data to be `sex`. We have done this and then "sex" is uniformly used throughout the paper. Even though we have changed the `gender` variable to be `sex`, we keep the explanation of the importance for the educators to emphasize the discussion between the usage of `sex` and `gender` because in many other cases and datasets, the usage between `sex` and `gender` are often interchangeable. XXX DONE

\begin{description}
\item[Associate Editor:] \textcolor{violet}{\textbf{The discussion around highest grade completed is mechanical in what was done, but lacks substantive reasoning for those decisions and possible downstream consequences.} It is still unclear to me whether education is measured by year or by category (it’s described both ways) and, in either case, the decision for one or the other isn’t contrasted or justified. For example `hcg` is described as a factor and `grade` is described as only increasing (numeric?) and surely the authors mean non-decreasing. If this is meant to be a case study for the classroom, this decision is rich ground for discussion.}
\end{description}

* We have added more explanation of the two variables, and suggestions of where to use one and the other in classroom analyses. XXX Dewi to do

@@

* Using `rlm` with the `nest` and `map` functions from `tidyr`, efficiently and simply fit these models. They can be easily explained in a classroom setting, and equip students generally with advanced data handling skills. Similar results would be obtained from using robustlmm, though. We have removed reference to memory and convergence issues. We have also removed a specific reference to threshold used. Having the particular number used is not important for the explanation of the approach and as we have seen from the review, is distracting for the reader. This section has been modified so that the approach is more understandable. XXX DONE

@@

* This is more of a comment than a request to make a change, but we agree that this is an area that could be a good classroom discussion. We have revised the section on handling extremes to make our explanation simpler, with links to the shiny app that we put together to assist in the judgment and choice of threshold. We hope that this provides fodder for discussion. It could definitely be worked into a teaching exercise. XXX DONE

@@

* It would be nice if the database contained a broader description of race, but it only has a single variable for the race. For this reason, our cleaned data reflects this and has a single variable for the race. We have explained why we used these categories and suggested the data provider adjust the race variable to use the current standard. XXX DONE

@@

* We have revised the introduction to fix this. XXX DONE

@@

* We have added additional bullet points on the benefit for educators in Section 5, in response to the overview comments by the Editor and AE (top of this response). We think it is best to keep content on cleaning and tidying the data, in a reproducible manner, to match the mission of the special issue. XXX DONE

@@

* We have changed all to "refresh" as it is not correct if we say it as a replication because we did not use the exactly same variable and same result (esepcially ID included in the dropouts cohort.) XXX DONE

@@

* Thanks for this, exactly right! We have changed the wording accordingly, in various places in the paper. XXX DC, ET, NT please check that this message comes across clearly enough.

@@

* Same point as made by the AE, and how we have addressed it is described above.

@@

* See response above to the associate editor, about this concern. XXX DONE

@@

* Done XXX Dewi

@@

* XXX Dewi Add some words to make it clear what data this is summarising

@@

* This sentence means that when the revised `hgc` variable were not reported, we only use the unrevised version of the `hgc` in that year. We thank the reviewer for this notice. We agree that this sentences is not clear, so we have modified it. XXX DONE

@@

\begin{description}
\item[Reviewer 2:] \textcolor{violet}{Some extraneous punctuation marks are present}
\begin{itemize}
  \item \textcolor{violet}{p1 in abstract: Both “wages textbook subset, have not” and “open source R package, called” do not need commas.}
  \item \textcolor{violet}{p2 “high school dropouts, from 1979-1994” does not need comma}
  \item \textcolor{violet}{p2 comma after “divergence of purpose” might be better replaced with dash.}
  \item \textcolor{violet}{p4 the sentence “Plot (C) shows the profile for an individual, with not such a high maximum wage but still indicates a problem: their wages are consistently low except for one year where they earned close to 1200/hour.” needs a few edits. I suggest “Plot (C) shows the profile for an individual with a maximum wage that is not so extreme but still indicates a problem: their wages are consistently low except for one year where they earned close to 1200/hour.”}
  \item \textcolor{violet}{p24 “predominately” does not need a hyphen.}
\end{itemize}
\end{description}

@@

\begin{description}
\item[Reviewer 2:] \textcolor{violet}{Punctuation should go inside quotation marks, not outside}
\begin{itemize}
\item \textcolor{violet}{p2 comma  “Applied longitudinal data analysis”,}
\item \textcolor{violet}{p4 comma “tame data”,}
\item \textcolor{violet}{p6 comma “statistical value chain”,}
\item \textcolor{violet}{p9 period “female”.}
\item \textcolor{violet}{p13 period “number of weeks worked since the last interview”.}
\end{itemize}
\end{description}

@@

\begin{description}
\item[Reviewer 2:] \textcolor{violet}{Miscellaneous comments:} 
\begin{itemize}
\item \textcolor{violet}{p6 “For example, use a single categorical race variable instead of the two binary race variables.” Perhaps missing a “we” before use?}
\item \textcolor{violet}{p6 The sentence beginning “van der Loo and de Jonge” is jarring because of the lowercase name, particularly because it starts a paragraph and section. I recommend flipping the clauses to begin “In the context of official statistics, van der Loo and de Jonge…”}
\item \textcolor{violet}{p18 “The year when the individual starting to work.” should perhaps be “The year when the individual started to work.”}
\item \textcolor{violet}{p24 The sentence “On an individual level, one needs to know where I am in this data and does this data relate to me.” needs edits. I’m not sure people from the longitudinal study are likely to be looking at this data, so “where I am in this data” is not quite accurate. Rather, people might want to see how their characteristics relate to those in the dataset.}
\item \textcolor{violet}{p26 Cooksey reference should have NLSY capitalized.} 
\end{itemize}
\end{description}

@@

\begin{description}
\item[Reviewer 1:] \textcolor{violet}{Minor comments:}
\begin{itemize}
\item \textcolor{violet}{P2, l46: missing right parenthesis.}
\item \textcolor{violet}{P9, l24: missing word(s) "this sometimes difficult the adjustment"}
\item \textcolor{violet}{P11, l43: "hours" worked}
\item \textcolor{violet}{P12, l32: unit in "weeks"}
\item \textcolor{violet}{P14, l38: Figure 3 shows...}
\item \textcolor{violet}{P21, l21: "the weeks worked since" ...}
\item \textcolor{violet}{P24, l21: The sentence "On an individual level, one needs to know where I am in this data and does this data relate to me" is awkward. Please revise.}
\item  \textcolor{violet}{P34 l 38: Figure 5 (C) is mislabeled}
\end{itemize}
\end{description}

@@

* We have put the capitalisation back in. Besides, we did not use the term "White" in the dataset as we used the same term reported in the database, which is "Non-Black, Non-Hispanic". XXX Done

\begin{description}
\item[Reviewer 3:] \textcolor{violet}{Page 7 lines 36-42:}
\begin{itemize}
\item \textcolor{violet}{1. The wages data of the whole NLSY79 cohort, including females.}
\item \textcolor{violet}{2. A separate table of the demographic data of the whole NLSY79 cohort.}
\item \textcolor{violet}{3. The high school dropouts’ wages data is closest to a refreshed version of Singer and Willett (2003)’s data.}
\end{itemize}
\textcolor{violet}{1 and 2 are nouns and 3 is a sentence – I’m a little confused what this third dataset represents.  I think you mean that you create a subset of (1) in the scope of the original data, to see how closely it replicates?}
\end{description}
